\vspace{-1in} \usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt] \huge A Security Analysis of the Lenel BlueDiamond \\

### 2020-05-05 paper/paper/paper.tex
fixed problem
add abstract, lets see how many things break

\begin{document}
\maketitle
\selectlanguage{english}
\begin{abstract}
The abstract is in a sense the most important part of your paper, since many readers will scan an abstract first before deciding to invest effort in reading the paper.

An abstract should be about 300 words long at most, and should act as a clear summary of the paper. It should state the aim and scope of the research, methods, results and conclusions, and the implications of the paper’s finding. The abstract should be broadly accessible (i.e. able to be understood by as many people as possible - even those outside the field) and communicate the importance of the work being done.

Structure the abstract as follows: background and aims, methods, results and conclusion.

Examples of some decent abstracts can be found \href{http://journal.stemfellowship.org/userimages/ContentEditor/1451371646443/AbstractExamples.pdf}{here}, with the main ideas highlighted.
\end{abstract}

>>>>

\begin{document}
\maketitle
\selectlanguage{english}
\begin{abstract}
Contactless authentication devices have existed in some capacity since the late 20th century. These devices allow users to authenticate themselves using something they have (smart card, proximity card, mobile device, etc) rather than something they know (passcode, combination, security question, etc) making the end-user less responsible for their authentication. This puts noticeably more pressure on the manufacturers to provide a product capable of providing confidentiality, integrity, and availability for its users. As such, the technology continues to advance as companies come up with newer, more advanced, ways to authenticate securely. In recent years, Lenel corporations has released multiple products under the BlueDiamond name that claim to "enhance freedom of movement in the workplace." /cite{lenelbluediamondwebsite} To date, these devices remain untested by the further research community for vulnerabilities that may lead to a breach of access control. As such, this paper aims to design an experimental process that future researchers may follow to accurately assess the security characteristics of Lenel's BlueDiamond contactless readers. This experiment will follow standard scientific procedure, using multiple tests to verify results and standard units of measurement to score success. Our analysis of these devices concludes that further testing on the subjects of Wiegand, RFID, Bluetooth, and the physical hardware may uncover significant findings.
\end{abstract}
